Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-01-22 paper.tex
Fixed tables and captions

\usepackage{float,fullpage}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}

@@

\section*{Abstract}

This paper investigates the effectiveness of the Forest Fire Danger Index (FFDI) \citep{mcarthur67} at predicting probability of ignition of bushfire in Victoria using logistic regression, classification trees and random forests. I construct a 10km gridded dataset of Victoria consisting of daily values for FFDI, temperature, wind speed, relative humidity, the drought factor, grassland curing level, vapour pressure at 9am and precipitation between 2000 and 2010. I find that the FFDI alone is a poor predictor of ignition. By adding the input variables to the FFDI, grassland curing, vapour pressure at 9am and precipitation I improve model accuracy and conclude that, of the variables used, grassland curing is the most important in predicting ignition. Combining non-linear regression splines with logistic models produces predictive performance comparable with random forests.

@@

McArthur’s FFDI originated as tabulated indices and were subsequently reduced to equations by \citet{noble80} which in turn simplified into the formulation of the FFDI given by equation (\ref{eq FFDI}).

\begin{equation}
\label{eq FFDI}
F=2.0 e^{-0.450 + 0.987 \ln(D)-0.0345H+0.0338T+0.0234V}
\end{equation}
where 
\begin{itemize}
	\item $D$: drought factor (Index)
	\item $H$: relative humidity (percent)
	\item $T$: temperature (degrees Celsius)
	\item $V$: Average wind velocity (\emph{km/hr})
\end{itemize}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{|c|c|}
		\hline Fire Danger Rating & Forest Fire Danger Index \\ 
		\hline
		Low-Moderate  & 0-11 \\ 
		High  &  12-24 \\ 
		Very High  &  25-49\\ 
		Severe &  50-74\\ 
		Extreme  &  75-99 \\ 
		Code Red  &  100+ \\ 
		\hline 
	\end{tabular}
	\caption{The Forest Fire Danger Index and the Fire Danger Rating}
	\label{table:FDR}
\end{table}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrrrrr}
		\hline
		& ffdi & temp & df & rh & ws & curing & rain & vap \\ 
		\hline
		ffdi & 1.00 & 0.77 & 0.62 & -0.77 & 0.04 & 0.51 & -0.20 & 0.01 \\ 
		temp & 0.77 & 1.00 & 0.43 & -0.70 & -0.18 & 0.46 & -0.10 & 0.39 \\ 
		df & 0.62 & 0.43 & 1.00 & -0.58 & -0.09 & 0.47 & -0.37 & -0.08 \\ 
		rh & -0.77 & -0.70 & -0.58 & 1.00 & 0.19 & -0.49 & 0.31 & 0.06 \\ 
		ws & 0.04 & -0.18 & -0.09 & 0.19 & 1.00 & 0.01 & 0.07 & -0.16 \\ 
		curing & 0.51 & 0.46 & 0.47 & -0.49 & 0.01 & 1.00 & -0.11 & 0.05 \\ 
		rain & -0.20 & -0.10 & -0.37 & 0.31 & 0.07 & -0.11 & 1.00 & 0.17 \\ 
		vap & 0.01 & 0.39 & -0.08 & 0.06 & -0.16 & 0.05 & 0.17 & 1.00 \\ 
		\hline
	\end{tabular}
	\caption{Correlation matrix of variables}
	\label{table:correl}
\end{table}

@@

For consistency all three of the classification techniques are estimated on the balanced training set and evaluated by  on the test data. I evaluate based on receiver operating characteristic (ROC) plots  and using 2 x 2 confusion matrices.

An example confusion matrix is given in table \ref{table:ex}. 
%eg confusion matrix with ABCD
\begin{table}[ht]
	\centering
	\begin{tabular}{r|rr|r}
		& Model & & \\ 
		\hline
		& Prediction   & &  \\ 
		Reference & No Fire & Fire & \\ 
		\hline
		No Fire & a & a & a+b \\ 
		Fire & c & d  & c + d \\ 
		\hline
		 & a+c & b+d & N \\
	\end{tabular}
	\caption{Example confusion matrix}
	\label{table:ex}
\end{table}

@@

I also report sensitivity (correctly classified fires dividied by total number of actual fires) and specificity (correctly identified non-fires divided by total number of non-fires), balanced accuracy and kappa.

\begin{equation}
\label{eq sens}
\mbox{Sensitivity} = \frac{a }{a+b}
\end{equation}

\begin{equation}
\label{eq spec}
\mbox{Specificity} = \frac{d}{c+d}
\end{equation}

\begin{equation}
\label{eq BA}
\mbox{Balanced Accuracy} = \frac{\frac{a }{a+b} + \frac{d}{c+d} }{2}
\end{equation}

\begin{equation}
\label{eq:K}
\kappa = \frac{P_0 - P_c}{1-P_c}
\end{equation}

where $P_0$ is the total agreement probability and $P_c$ is the “agreement” probability which is due to chance ( see \cite{kappa} for definitions )

@@

%**How to do LR test on diff num observations? 
% Table: Regression output
\begin{table}
	\begin{center}
		\begin{tabular}{l c c c }
			\hline
			& Model 1 & Model 2 & Model 3 \\
		\hline
		(Intercept)    & $-0.1050^{***}$ & $-18.2314^{***}$ & $-15.4002^{***}$ \\
		& $(0.0204)$      & $(1.0391)$       & $(1.4012)$       \\
		ffdi           & $0.0073^{***}$  & $-0.0423^{***}$  & $-0.0370^{***}$  \\
		& $(0.0011)$      & $(0.0025)$       & $(0.0028)$       \\
		temp           &                 & $0.0604^{***}$   & $0.0504^{***}$   \\
		&                 & $(0.0034)$       & $(0.0048)$       \\
		rh             &                 & $-0.0100^{***}$  & $-0.0103^{***}$  \\
		&                 & $(0.0013)$       & $(0.0015)$       \\
		ws             &                 & $0.0666^{***}$   & $0.0687^{***}$   \\
		&                 & $(0.0074)$       & $(0.0082)$       \\
		df             &                 & $0.1084^{***}$   & $0.0682^{***}$   \\
		&                 & $(0.0072)$       & $(0.0084)$       \\
		curing         &                 &                  & $0.0012$         \\
		&                 &                  & $(0.0006)$       \\
		rain           &                 &                  & $-0.0525^{***}$  \\
		&                 &                  & $(0.0057)$       \\
		vap            &                 &                  & $0.0244^{***}$   \\
		&                 &                  & $(0.0062)$       \\
		\hline
		AIC            & 31809.3877      & 31229.3462       & 26589.0141       \\
		BIC            & 31825.4721      & 31277.5994       & 26659.9683       \\
		Log Likelihood & -15902.6938     & -15608.6731      & -13285.5071      \\
		Deviance       & 31805.3877      & 31217.3462       & 26571.0141       \\
		Num. obs.      & 22976           & 22976            & 19610            \\
		\hline
		\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
	\end{tabular}
	\caption{Logistic regressions output}
	\label{table:coefficients}
\end{center}
\end{table}

@@

%Output from best performing splines model (used xtable rather than texreg, too inconsistent?)
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrr}
		\hline
		& Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
		\hline
		(Intercept) & -3.1484 & 0.2757 & -11.4210 & 0.0000 \\ 
		ns(ffdi, 5)1 & -0.2905 & 0.3613 & -0.8043 & 0.4213 \\ 
		ns(ffdi, 5)2 & -0.2304 & 0.4625 & -0.4982 & 0.6183 \\ 
		ns(ffdi, 5)3 & 0.4040 & 0.5589 & 0.7229 & 0.4697 \\ 
		ns(ffdi, 5)4 & -0.4340 & 0.9674 & -0.4487 & 0.6537 \\ 
		ns(ffdi, 5)5 & -0.8815 & 0.7271 & -1.2124 & 0.2254 \\ 
		ns(temp, 1) & 1.8543 & 0.3416 & 5.4276 & 0.0000 \\ 
		ns(rh, 2)1 & 0.9325 & 0.5687 & 1.6397 & 0.1011 \\ 
		ns(rh, 2)2 & -0.6173 & 0.3607 & -1.7115 & 0.0870 \\ 
		ws & -0.0169 & 0.0146 & -1.1541 & 0.2485 \\ 
		ns(df, 5)1 & 1.1093 & 0.2798 & 3.9639 & 0.0001 \\ 
		ns(df, 5)2 & 1.0156 & 0.3115 & 3.2601 & 0.0011 \\ 
		ns(df, 5)3 & 0.7113 & 0.2604 & 2.7319 & 0.0063 \\ 
		ns(df, 5)4 & 0.8071 & 0.5479 & 1.4730 & 0.1408 \\ 
		ns(df, 5)5 & -0.1512 & 0.1950 & -0.7752 & 0.4382 \\ 
		ns(curing, 6)1 & 1.5648 & 0.1388 & 11.2754 & 0.0000 \\ 
		ns(curing, 6)2 & 2.3986 & 0.1874 & 12.7997 & 0.0000 \\ 
		ns(curing, 6)3 & 1.6637 & 0.1640 & 10.1436 & 0.0000 \\ 
		ns(curing, 6)4 & 1.6949 & 0.1335 & 12.6921 & 0.0000 \\ 
		ns(curing, 6)5 & 1.4634 & 0.3436 & 4.2588 & 0.0000 \\ 
		ns(curing, 6)6 & -0.4909 & 0.0817 & -6.0066 & 0.0000 \\ 
		rain & -0.0286 & 0.0056 & -5.0703 & 0.0000 \\ 
		vap & -0.0003 & 0.0067 & -0.0504 & 0.9598 \\ 
		\hline
	\end{tabular}
	\caption{Regression output for Model 4}
	\label{table:logf}
\end{table}

@@

%Confusion matrix cutoff=0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{r|rr|rr|rr|rr}
		\hline
		& Model 1 &  & Model 2 &  & Model 3 &  & Model 4 & \\ 
		\hline
		& Actual   &  &  &  &  & & & \\ 
		Predict & No Fire & Fire & No Fire & Fire & No Fire & Fire & No Fire & Fire\\ 
		\hline
No Fire & 0.5959 & 0.0030 & 0.4457 & 0.0019 & 0.5111 & 0.0021 & 0.5807 & 0.0016 \\ 
Fire & 0.3989 & 0.0022 & 0.5490 & 0.0034 & 0.4838 & 0.0030 & 0.4142 & 0.0035 \\ 
		\hline
	\end{tabular}
	\caption{Confusion Matrices for Models 1, 2 \& 3 cutoff value 0.5}
	\label{table:cm2}
\end{table}

% Accuracy for cutoff 0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrr}
		\hline
		& 1 & 2 & 3 & 4 \\ 
		\hline
Sensitivity & 0.5990 & 0.4481 & 0.5137 & 0.5837 \\ 
Specificity & 0.4267 & 0.6476 & 0.5854 & 0.6920 \\ 
Balanced Accuracy & 0.5129 & 0.5479 & 0.5495 & 0.6378 \\ 
Accuracy & 0.5981 & 0.4492 & 0.5141 & 0.5842 \\ 
Kappa & 0.0007 & 0.0018 & 0.0021 & 0.0067 \\
		\hline
	\end{tabular}
		\caption{Accuracy for Models 1, 2, 3 \& 4 cutoff value 0.5}
		\label{table:acc2}
\end{table}

@@

%Confusion matrix cutoff=0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{r|rr|rr}
		\hline
		  & Tree 1 &  & Tree 2 & \\ 
		\hline
		& Actual   &  &  &   \\ 
		Predict  & No Fire & Fire & No Fire & Fire\\ 
		\hline
No Fire  & 0.5553 & 0.0017 & 0.5088 & 0.0014 \\ 
Fire  & 0.4394 & 0.0036 & 0.4859 & 0.0038 \\ 
		\hline
	\end{tabular}
	\caption{Confusion Matrices for trees cutoff value 0.5}
	\label{table:tcm2}
\end{table}

% Accuracy for cutoff 0.5
\begin{table}[H]
	\centering
	\begin{tabular}{rrr}
		\hline
		 & Tree 1 & Tree 2 \\ 
		\hline
		Sensitivity  & 0.5582 & 0.5115 \\ 
		Specificity & 0.6832 & 0.7273 \\  
		Balanced Accuracy  & 0.6207 & 0.6194 \\ 
		Accuracy  & 0.5589 & 0.5127 \\ 
		Kappa & 0.0055 & 0.0051 \\ 
		\hline
	\end{tabular}
	\caption{Accuracy for trees cutoff value 0.5}
	\label{table:tacc2}
\end{table}

@@

%confusion matrix on 0.5 cutoff value
\begin{table}[ht]
	\centering
	\begin{tabular}{rrr}
		\hline
		& Random Forest &  \\ 
		\hline
		& Actual   &   \\ 
		Predict  & No Fire & Fire \\ 
		\hline
		No Fire & 0.6093 & 0.0016 \\ 
		Fire & 0.3856 & 0.0035 \\ 
		\hline
	\end{tabular}
		\caption{Confusion matrix for random forest cutoff value 0.5}
		\label{table:cmrf}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{rr}
		\hline
		& Random Forest \\ 
		\hline
		Sensitivity & 0.6124 \\ 
		Specificity & 0.6771 \\ 
		Balanced Accuracy & 0.6447 \\ 
		Accuracy & 0.6127 \\ 
		Kappa & 0.0075 \\ 
		\hline
	\end{tabular}
			\caption{Accuracy measure random forest cutoff value 0.5}
			\label{table:accrf}
\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{r|rrrr}
		\hline
		& Model 3 & Model 4 & Tree & Forest \\ 
		\hline
		AUC & 0.58 & 0.69 & 0.65 & 0.70 \\ 
		\hline
	\end{tabular}
	\caption{Areas under ROC curve for logistic model, classification trees \& forest}
	\label{table:AUC}
\end{table}

>>>>

\usepackage{fullpage,booktabs,amsmath}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}

%% FLOATS and CAPTIONS
\usepackage{float,caption}
\DeclareCaptionStyle{italic}[justification=centering]
 {labelfont={bf},textfont={it},labelsep=colon}
\captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
\captionsetup[table]{style=italic,format=hang,singlelinecheck=true}

%% GRAPHICS
\usepackage{graphicx}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

@@

\begin{abstract}
This paper investigates the effectiveness of the Forest Fire Danger Index (FFDI) \citep{mcarthur67} at predicting probability of ignition of bushfire in Victoria using logistic regression, classification trees and random forests. I construct a 10km gridded dataset of Victoria consisting of daily values for FFDI, temperature, wind speed, relative humidity, the drought factor, grassland curing level, vapour pressure at 9am and precipitation between 2000 and 2010. I find that the FFDI alone is a poor predictor of ignition. By adding the input variables to the FFDI, grassland curing, vapour pressure at 9am and precipitation I improve model accuracy and conclude that, of the variables used, grassland curing is the most important in predicting ignition. Combining non-linear regression splines with logistic models produces predictive performance comparable with random forests. 
\end{abstract}

@@

McArthur’s FFDI originated as tabulated indices and were subsequently reduced to equations by \citet{noble80} which in turn simplified into the formulation of the FFDI given by
\begin{equation}
\label{eq FFDI}
F=2.0 e^{-0.450 + 0.987 \ln(D)-0.0345H+0.0338T+0.0234V},
\end{equation}
where 
\begin{itemize}
	\item $D$ is the drought factor index;
	\item $H$ is relative humidity (as a percentage);
	\item $T$ is temperature (degrees Celsius); and
	\item $V$ is average wind velocity (in km/hr).
\end{itemize}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{ll}
		\toprule
		Fire Danger Rating & Forest Fire Danger Index \\
		\midrule
		Low-Moderate              & 0--11 \\
		High                      & 12--24 \\
		Very High                 & 25--49\\
		Severe                    & 50--74\\
		Extreme                   & 75--99 \\
		Code Red                  & 100+ \\
		\bottomrule
	\end{tabular}
	\caption{The Forest Fire Danger Index and the Fire Danger Rating}
	\label{table:FDR}
\end{table}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{lrrrrrrrr}
		\toprule
		       & ffdi  & temp  & df    & rh    & ws    & curing & rain  & vap \\
		\midrule
		ffdi   & 1.00  & 0.77  & 0.62  & -0.77 & 0.04  & 0.51   & -0.20 & 0.01 \\
		temp   & 0.77  & 1.00  & 0.43  & -0.70 & -0.18 & 0.46   & -0.10 & 0.39 \\
		df     & 0.62  & 0.43  & 1.00  & -0.58 & -0.09 & 0.47   & -0.37 & -0.08 \\
		rh     & -0.77 & -0.70 & -0.58 & 1.00  & 0.19  & -0.49  & 0.31  & 0.06 \\
		ws     & 0.04  & -0.18 & -0.09 & 0.19  & 1.00  & 0.01   & 0.07  & -0.16 \\
		curing & 0.51  & 0.46  & 0.47  & -0.49 & 0.01  & 1.00   & -0.11 & 0.05 \\
		rain   & -0.20 & -0.10 & -0.37 & 0.31  & 0.07  & -0.11  & 1.00  & 0.17 \\
		vap    & 0.01  & 0.39  & -0.08 & 0.06  & -0.16 & 0.05   & 0.17  & 1.00 \\
		\bottomrule
	\end{tabular}
	\caption{Correlation matrix of variables}
	\label{table:correl}
\end{table}

@@

For consistency all three of the classification techniques are estimated on the balanced training set and evaluated by  on the test data. I evaluate based on receiver operating characteristic (ROC) plots  and using $2\times2$ confusion matrices.

An example confusion matrix is given in Table~\ref{table:ex}. 
%eg confusion matrix with ABCD
\begin{table}[ht]
	\centering
	\begin{tabular}{lr|rr|r|}
    & 	\multicolumn{1}{l}{} & \multicolumn{2}{c}{\emph{Model Prediction}} \\
    & 	\multicolumn{1}{l}{} & \multicolumn{1}{r}{No Fire} & \multicolumn{1}{r}{Fire} \\
		\cline{3-5}
\emph{Actual} & No Fire & a   & a   & a+b \\
                 & 		Fire & c   & d   & c + d \\
		\cline{3-5}
                 & 		     & a+c & b+d & N \\
		\cline{3-5}
	\end{tabular}
	\caption{Example confusion matrix}
	\label{table:ex}
\end{table}

@@

I also report sensitivity (correctly classified fires dividied by total number of actual fires) and specificity (correctly identified non-fires divided by total number of non-fires), balanced accuracy and kappa:
\begin{align}
\label{eq sens}
\mbox{Sensitivity} &= \frac{a }{a+b} \\
\label{eq spec}
\mbox{Specificity} &= \frac{d}{c+d} \\
\label{eq BA}
\mbox{Balanced Accuracy} &= \frac{\frac{a }{a+b} + \frac{d}{c+d} }{2} \\
\label{eq:K}
\kappa &= \frac{P_0 - P_c}{1-P_c}
\end{align}
where $P_0$ is the total agreement probability and $P_c$ is the “agreement” probability which is due to chance ( see \cite{kappa} for definitions )

@@

%**How to do LR test on diff num observations? 
% Table: Regression output
\begin{table}
	\begin{center}
		\begin{tabular}{llll}
			\toprule
			& Model 1 & Model 2 & Model 3 \\
		\midrule
		(Intercept)    & $-0.1050^{***}$ & $-18.2314^{***}$ & $-15.4002^{***}$ \\
		& $(0.0204)$      & $(1.0391)$       & $(1.4012)$       \\
		ffdi           & $0.0073^{***}$  & $-0.0423^{***}$  & $-0.0370^{***}$  \\
		& $(0.0011)$      & $(0.0025)$       & $(0.0028)$       \\
		temp           &                 & $0.0604^{***}$   & $0.0504^{***}$   \\
		&                 & $(0.0034)$       & $(0.0048)$       \\
		rh             &                 & $-0.0100^{***}$  & $-0.0103^{***}$  \\
		&                 & $(0.0013)$       & $(0.0015)$       \\
		ws             &                 & $0.0666^{***}$   & $0.0687^{***}$   \\
		&                 & $(0.0074)$       & $(0.0082)$       \\
		df             &                 & $0.1084^{***}$   & $0.0682^{***}$   \\
		&                 & $(0.0072)$       & $(0.0084)$       \\
		curing         &                 &                  & $0.0012$         \\
		&                 &                  & $(0.0006)$       \\
		rain           &                 &                  & $-0.0525^{***}$  \\
		&                 &                  & $(0.0057)$       \\
		vap            &                 &                  & $0.0244^{***}$   \\
		&                 &                  & $(0.0062)$       \\
		\midrule
		AIC            & 31809.3877      & 31229.3462       & 26589.0141       \\
		BIC            & 31825.4721      & 31277.5994       & 26659.9683       \\
		Log Likelihood & -15902.6938     & -15608.6731      & -13285.5071      \\
		Deviance       & 31805.3877      & 31217.3462       & 26571.0141       \\
		Num. obs.      & 22976           & 22976            & 19610            \\
		\bottomrule
		\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
	\end{tabular}
	\caption{Logistic regressions output}
	\label{table:coefficients}
\end{center}
\end{table}

@@

%Output from best performing splines model (used xtable rather than texreg, too inconsistent?)
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrr}
		\toprule
		& Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
		\midrule
		(Intercept) & -3.1484 & 0.2757 & -11.4210 & 0.0000 \\ 
		ns(ffdi, 5)1 & -0.2905 & 0.3613 & -0.8043 & 0.4213 \\ 
		ns(ffdi, 5)2 & -0.2304 & 0.4625 & -0.4982 & 0.6183 \\ 
		ns(ffdi, 5)3 & 0.4040 & 0.5589 & 0.7229 & 0.4697 \\ 
		ns(ffdi, 5)4 & -0.4340 & 0.9674 & -0.4487 & 0.6537 \\ 
		ns(ffdi, 5)5 & -0.8815 & 0.7271 & -1.2124 & 0.2254 \\ 
		ns(temp, 1) & 1.8543 & 0.3416 & 5.4276 & 0.0000 \\ 
		ns(rh, 2)1 & 0.9325 & 0.5687 & 1.6397 & 0.1011 \\ 
		ns(rh, 2)2 & -0.6173 & 0.3607 & -1.7115 & 0.0870 \\ 
		ws & -0.0169 & 0.0146 & -1.1541 & 0.2485 \\ 
		ns(df, 5)1 & 1.1093 & 0.2798 & 3.9639 & 0.0001 \\ 
		ns(df, 5)2 & 1.0156 & 0.3115 & 3.2601 & 0.0011 \\ 
		ns(df, 5)3 & 0.7113 & 0.2604 & 2.7319 & 0.0063 \\ 
		ns(df, 5)4 & 0.8071 & 0.5479 & 1.4730 & 0.1408 \\ 
		ns(df, 5)5 & -0.1512 & 0.1950 & -0.7752 & 0.4382 \\ 
		ns(curing, 6)1 & 1.5648 & 0.1388 & 11.2754 & 0.0000 \\ 
		ns(curing, 6)2 & 2.3986 & 0.1874 & 12.7997 & 0.0000 \\ 
		ns(curing, 6)3 & 1.6637 & 0.1640 & 10.1436 & 0.0000 \\ 
		ns(curing, 6)4 & 1.6949 & 0.1335 & 12.6921 & 0.0000 \\ 
		ns(curing, 6)5 & 1.4634 & 0.3436 & 4.2588 & 0.0000 \\ 
		ns(curing, 6)6 & -0.4909 & 0.0817 & -6.0066 & 0.0000 \\ 
		rain & -0.0286 & 0.0056 & -5.0703 & 0.0000 \\ 
		vap & -0.0003 & 0.0067 & -0.0504 & 0.9598 \\ 
		\bottomrule
	\end{tabular}
	\caption{Regression output for Model 4}
	\label{table:logf}
\end{table}

@@

%Confusion matrix cutoff=0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{r|rr|rr|rr|rr}
		\toprule
		& Model 1 &  & Model 2 &  & Model 3 &  & Model 4 & \\ 
		\midrule
		& Actual   &  &  &  &  & & & \\ 
		Predict & No Fire & Fire & No Fire & Fire & No Fire & Fire & No Fire & Fire\\ 
		\midrule
No Fire & 0.5959 & 0.0030 & 0.4457 & 0.0019 & 0.5111 & 0.0021 & 0.5807 & 0.0016 \\ 
Fire & 0.3989 & 0.0022 & 0.5490 & 0.0034 & 0.4838 & 0.0030 & 0.4142 & 0.0035 \\ 
		\bottomrule
	\end{tabular}
	\caption{Confusion Matrices for Models 1, 2 \& 3 cutoff value 0.5}
	\label{table:cm2}
\end{table}

% Accuracy for cutoff 0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrr}
		\toprule
		& 1 & 2 & 3 & 4 \\ 
		\midrule
Sensitivity & 0.5990 & 0.4481 & 0.5137 & 0.5837 \\ 
Specificity & 0.4267 & 0.6476 & 0.5854 & 0.6920 \\ 
Balanced Accuracy & 0.5129 & 0.5479 & 0.5495 & 0.6378 \\ 
Accuracy & 0.5981 & 0.4492 & 0.5141 & 0.5842 \\ 
Kappa & 0.0007 & 0.0018 & 0.0021 & 0.0067 \\
		\bottomrule
	\end{tabular}
		\caption{Accuracy for Models 1, 2, 3 \& 4 cutoff value 0.5}
		\label{table:acc2}
\end{table}

@@

%Confusion matrix cutoff=0.5
\begin{table}[ht]
	\centering
	\begin{tabular}{r|rr|rr}
		\toprule
		  & Tree 1 &  & Tree 2 & \\ 
		\midrule
		& Actual   &  &  &   \\ 
		Predict  & No Fire & Fire & No Fire & Fire\\ 
		\midrule
No Fire  & 0.5553 & 0.0017 & 0.5088 & 0.0014 \\ 
Fire  & 0.4394 & 0.0036 & 0.4859 & 0.0038 \\ 
		\bottomrule
	\end{tabular}
	\caption{Confusion Matrices for trees cutoff value 0.5}
	\label{table:tcm2}
\end{table}

% Accuracy for cutoff 0.5
\begin{table}[H]
	\centering
	\begin{tabular}{rrr}
		\toprule
		 & Tree 1 & Tree 2 \\ 
		\midrule
		Sensitivity  & 0.5582 & 0.5115 \\ 
		Specificity & 0.6832 & 0.7273 \\  
		Balanced Accuracy  & 0.6207 & 0.6194 \\ 
		Accuracy  & 0.5589 & 0.5127 \\ 
		Kappa & 0.0055 & 0.0051 \\ 
		\bottomrule
	\end{tabular}
	\caption{Accuracy for trees cutoff value 0.5}
	\label{table:tacc2}
\end{table}

@@

%confusion matrix on 0.5 cutoff value
\begin{table}[ht]
	\centering
	\begin{tabular}{rrr}
		\toprule
		& Random Forest &  \\ 
		\midrule
		& Actual   &   \\ 
		Predict  & No Fire & Fire \\ 
		\midrule
		No Fire & 0.6093 & 0.0016 \\ 
		Fire & 0.3856 & 0.0035 \\ 
		\bottomrule
	\end{tabular}
		\caption{Confusion matrix for random forest cutoff value 0.5}
		\label{table:cmrf}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{rr}
		\toprule
		& Random Forest \\ 
		\midrule
		Sensitivity & 0.6124 \\ 
		Specificity & 0.6771 \\ 
		Balanced Accuracy & 0.6447 \\ 
		Accuracy & 0.6127 \\ 
		Kappa & 0.0075 \\ 
		\bottomrule
	\end{tabular}
			\caption{Accuracy measure random forest cutoff value 0.5}
			\label{table:accrf}
\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{r|rrrr}
		\toprule
		& Model 3 & Model 4 & Tree & Forest \\ 
		\midrule
		AUC & 0.58 & 0.69 & 0.65 & 0.70 \\ 
		\midrule
	\end{tabular}
	\caption{Areas under ROC curve for logistic model, classification trees \& forest}
	\label{table:AUC}
\end{table}
